{\LARGE Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-28 Paper/main.tex
Equations for FPCA

	The $\xi_j(\omega)$ are then given as $\xi_j(\omega) = \langle F(\omega) - \mu, \nu_j\rangle$ and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.

@@

	\begin{equation}\label{basis_exp_transf}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[\sum_{k \in \mathcal{L}} c_j d_k(\omega) \textcolor{teal}{ \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
			= \alpha + \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} c_j d_k(\omega)  \textcolor{teal}{Z_{j, k}} + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} \sum_{k = 1}^{K} c_j d_k(\omega) \textcolor{violet}{Z_{j, k}}  + \epsilon(\omega)	
		\end{split}
	\end{equation}

	A typical choice in this scenario is to use the same functional basis and the same truncation parameter for both the coefficient function and the approximation of the observations. This leads to the following simplification of Equation \ref{basis_exp_transf}.

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
			& \approx \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j = 1}^{L} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k  = 1}^{L} d_k(\omega)  \phi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j = 1}^{L} \left[\sum_{k = 1}^{L} c_j d_k(\omega) \textcolor{teal}{ \int_{0}^{1} \phi_j(s) 	\phi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
			= \alpha + \sum_{j = 1}^{L} \sum_{k = 1}^{L}  c_j d_k(\omega)\textcolor{teal}{Z_{j, k}}  + 	\epsilon(\omega)	
		\end{split}
	\end{equation}

>>>>

	The $\xi_j(\omega)$ are then given as 
	\begin{equation}
		\xi_j(\omega) = \langle F(\omega) - \mu, \nu_j\rangle = \int_{0}^{1} \left(F(\omega)(s) - \mu(s)\right) \nu_j(s) \mathrm{d}s
	\end{equation} 
	and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.

@@

	\begin{equation}\label{basis_exp_transf}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} c_j \left[\sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega) 
			= \alpha + \sum_{j \in \mathcal{I}} \left[ c_j \sum_{k \in \mathcal{L}} \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j {\color{violet}\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega) 
			= \alpha + \sum_{j = 1}^{J} c_j {\color{violet}\tilde{Z}_j(\omega)} + \epsilon(\omega) 
		\end{split}
	\end{equation}

	A typical choice in this scenario is to use the same functional basis and the same truncation parameter $L$ for both the coefficient function and the approximation of the observations. This leads to the following simplification of Equation \ref{basis_exp_transf}.

	\begin{equation}
		\begin{split}
			Z_{j, k}(\omega) & = d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
			\tilde{Z}_j(\omega) & = \sum_{k = 1}^{L} \left[d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
		\end{split}
	\end{equation}

	\subsection{Regression using Functional Principal Components}

	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{j, i} & = \int_{0}^{1} \left({\color{red} f_i(s) - \hat{\mu}(s)}\right) {\color{blue}\hat{\nu}(s)} \mathrm{d}s
			= \int_{0}^{1} \left({\color{red}\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)}\right) \left({\color{blue}\sum_{k \in \mathcal{L}} b_{k} \psi_{k}(s)}\right) \mathrm{d}s \\
			& = \sum_{j \in \mathcal{I}} \left[a_{i,j} \sum_{k \in \mathcal{L}} {\color{teal} b_{k} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
			= \sum_{j \in \mathcal{I}} \left[a_{i,j} \sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}} \right]\\
			&\approx \sum_{j = 1}^{J} \left[a_{i,j} {\color{violet}\sum_{k = 1}^{K} Z_{j,k}}  \right]
			= \sum_{j = 1}^{J} a_{i,j} {\color{violet}\tilde{Z}_{j}}
		\end{split}
	\end{equation}

	Again using the same basis and the same truncation parameter $L$ leads to the following simplifications of Equation \ref{FPCA_basis_expansion}.

	\begin{equation}
		\begin{split}
			Z_{j, k} & = d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
			\tilde{Z}_j& = \sum_{k = 1}^{L} \left[b_k \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
		\end{split}
	\end{equation}
